### 2009-06-09 talk/icooolps2009-dotnet/conclusion.tex
fix last davide's comment
try to incorporate some of the reviewers' comments
apply ACM categories, add copyright info and acknowledgements (mostly stolen from cfbolz :-))

Flexswitches are closely related to the concept of \emph{promotion}, as
described by \cite{PyPyJIT}, \cite{PyPyJIT09}.
Psyco is
a run-time specialiser for Python that uses promotion (called ``unlift'' in
\cite{DBLP:conf/pepm/Rigo04}). However, Psyco is a manually written JIT, is
not applicable to other languages and cannot be retargetted.

The idea of promotion is a generalization of \emph{Polymorphic
  Inline Caches} \cite{hoelzle_optimizing_1991}, as well as the idea of using
runtime feedback to produce more efficient code
\cite{hoelzle_type_feedback_1994}.

@@

\anto{XXX: please review the last two paragraphs}

@@

>>>>

Flexswitches are closely related to the concept of \emph{promotion}, as
described by \cite{PyPyJIT}, \cite{PyPyJIT09}.
Psyco is
a run-time specialiser for Python that uses promotion (called ``unlift'' in
\cite{DBLP:conf/pepm/Rigo04}). However, Psyco is a manually written JIT, is
not applicable to other languages and cannot be retargetted.  Psyco is a 
good example of how to implement flexswitches for targets that don't have the
limitations of the CLI.

The idea of promotion is a generalization of \emph{Polymorphic
  Inline Caches} \cite{hoelzle_optimizing_1991}, as well as the idea of using
runtime feedback to produce more efficient code
\cite{hoelzle_type_feedback_1994}.  The main difference between the two is 
that PICs only works on types, whereas promotion can work on every kind of value.

@@

@@

\section*{Acknowledgements}

The authors would like to thank Carl Friedrich Bolz, Maciej Fijalkowski and
the referees of ICOOOLPS'09 for helpful comments on earlier versions of this
paper.
